---
title: "Pulse Rate"
format: html
editor: visual
execute: 
  echo: false
  warning: false
---

```{r}
library(tidyverse)
library(primer.data)
library(rstanarm)
```

```{r}
x <- nhanes |> 
  select(pulse, gender) |> 
  drop_na() |> 
  filter(gender == "Female")

```

What is the difference in pulse rate between two randomly selected female students in this class?

```{r}
summary(x)
```

```{r}
fit_obj <- stan_glm(data = x,
         formula = pulse ~ 1,
         family = gaussian,
         refresh = 0,
         seed = 17)
```

```{r}
newobs <- tibble(.rows = 2)
pp <- posterior_predict(object = fit_obj,
                        newdata = newobs) |> 
  as_tibble() |> 
  mutate(diff  = abs(`1` - `2`))
  
```


```{r}
pp |> 
  ggplot(aes(x = diff)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100) +
  labs(title = "Posterior for the Pulse Difference Between Two Women",
       subtitle = "Uncertainty for individual difference is much greater than for the expected value",
       x = "Pulse",
       y = "Probability",
       caption = "Source: NANES") +
  scale_x_continuous(labels = scales::number_format()) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.5)) +
  theme_classic()
```

## Wisdom

predictive or causal
units - women outcome - pulse rate 
covariates
treatment only applies to causal
Preceptor Table - organization of data validity Population Table

why does validity fails?

## Justice

Justice is the second Cardinal Virtue in data science. Justice starts with the Population Table -- the data we want to have, the data which we actually have, and all the other data from that same population. Each row of the Population Table is defined by a unique Unit/Time combination. We explore three key issues about the Population Table. First, does the relationship among the variables demonstrate stability, meaning is the model stable across different time periods? Second, are the rows associated with the data representative of all the units which we might have had data for from that time period? Third, for causal models only, we consider unconfoundedness. Justice concludes by making an assumption about the data generating mechanism. Which general mathematical formula connects the outcome variable we are interested in with the other data that we have?

Stability Stability means that the relationship between the columns in the Population Table is the same for three categories of rows: the data, the Preceptor Table, and the larger population from which both are drawn.

unconfoundedness?

Representativeness Representativeness or the lack thereof, is the relationship, among the rows in the Population Table, between our data and the other rows. Ideally, we would like our data to be a random sample from the population. Sadly, this is almost never the case.

formula: pulse ~ 1

## Courage

Courage is the third Cardinal Virtue in data science. Justice gave us the data and the structure of the model. Courage allows us to explore different models. Even though Justice has provided the basic mathematical structure of the model, we still need to decide which variables to include and to estimate the values of unknown parameters. We avoid hypothesis tests. We check our models for consistency with the data we have. We select one model.


## Temperance
